Estimating Gaze Duration Error from Eye Tracking Data

### 2022-09-26 paper/paper.tex
Adding refs and lit review

Gaze fixation models will typically have an error profile that is dependent on both 
the nature of the media being presented, the variety of faces and lighting conditions 
in the training data. In addition, it has been observed that the error profile varies 
depending on the location of the true fixation point within the subjects field of view.
The errors in fixation point measurement for a given eye tracking solution are routinely
adjusted through a process called calibration. Improvements in the callibration process
are an ongoing focus for the development of algorithms\cite{Zhang2014,Hassoumi2019} 
and software tools\cite{ETCAL2018}. In some scenarios there are additional considerations
such as whether to use fixation data from individual eyes, or a composite 
signal\cite{Hooge2019}.

Discuss error elments around accuracy and precision \cite{Holmqvist2022}

>>>>

Gaze fixation models will typically have an error profile that is dependent on both 
the nature of the media being presented, the variety of faces and lighting conditions 
in the training data. In addition, it has been observed that the error profile varies 
depending on the location of the true fixation point within the subjects field of view.
The errors in fixation point measurement for a given eye tracking solution are routinely
monitored and adjusted through a process called calibration, in which users are presented
a series or \it{required fixation locations} (RFL) which are compared with measured 
points of fixation\cite{Hornof2002}. 
Improvements in the callibration process
are an ongoing focus for the development of algorithms\cite{Zhang2014,Hassoumi2019} 
and software tools\cite{ETCAL2018}. In some scenarios there are additional considerations
such as whether to use fixation data from individual eyes, or a composite 
signal\cite{Hooge2019}.

Typically the nature of the error detected in the calibration process can be broken
into both accuracy and precisions. Wherein accuracy is the tendency for the measure
fixation points to be closer to true fixation, and precision is the tendency for the
measured locations to vary for a given true fixation\cite{Holmqvist2022}. This distinction
is critical because it forms the basis of methods that can correct for the kind of 
systematic bias observed with low precision eye tracking.
